### 2016-01-16 paper.tex
Start line numbers from beginning; resolves #34
Clean up strut drag motivation

\begin{document}
\vspace*{0.35in}

@@

\linenumbers

@@

The present task was to acquire a new dataset for the lower solidity RM2
turbine, but at higher Reynolds numbers than those achieved in the experiments
at SAFL. It is also suspected that the strut drag model in CACTUS could be the
source of some discrepancy. The strut drag was deliberately modified in the
physical model to provide data to help answer that question. This dataset is
publicly available for both validation of CACTUS and other numerical models
\cite{Bachant2015-RM2-data}.

>>>>

\begin{document}
\linenumbers
\vspace*{0.35in}

@@

@@

The present task was to acquire a new dataset for the lower solidity RM2
turbine, but at higher Reynolds numbers than those achieved in the experiments
at SAFL. It was suspected that the strut drag model in CACTUS could be the
source of some discrepancy. Thus, the strut drag was deliberately and
significantly increased in the physical model to provide data to help answer
that question. This dataset is publicly available for both validation of CACTUS
and other numerical models \cite{Bachant2015-RM2-data}.
